Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Make list of contributions more consistent

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest, and extended
    Haddock's markup to support examples, back in 2010
\item
    Add support for QuickCheck properties to Doctest and
    extend Haddock markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

\item
    Introduce a set of combinators to express expectations about
    code examples for use with Hspec (Section \ref{sec:code-doc} and Section \ref{sec:hspec-comb})

\item
    Improve CI support for Doctest and Hspec (Section \ref{sec:TBD})

@@

\item
    Show best current practice of BDD in Haskell, using Doctest and
    Hspec (Section \ref{ref:Best-current-practice})

>>>>

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest, and
    extended Haddock's markup to support examples, back in 2010
\item
    We added support for QuickCheck properties to Doctest and extended
    Haddock's markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

\item
    We introduce a set of combinators to express expectations about
    code examples for use with Hspec (Section \ref{sec:code-doc} and
    Section \ref{sec:hspec-comb})

\item
    We improve CI support for Doctest and Hspec (Section
    \ref{sec:TBD})

@@

\item
    We show best current practice of BDD in Haskell, using Doctest and
    Hspec (Section \ref{ref:Best-current-practice})
